### 2021-10-26 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betadiversity_response@20a20e3718237e86663379d645b2d33c4128342a 🚀

This approach has been widely adopted since its publication, with recent
examples using it to understand the effect of fire on pollination
systems (Baronio \emph{et al.} 2021); the impact of rewiring on
spatio-temporal network dynamics (Campos-Moreno \emph{et al.} 2021); the
effects of farming on rural and urban landscapes on species interactions
(Olsson \emph{et al.} 2021); the impact of environment gradients on
multi-trophic metacommunities (\textbf{Ohlmann2018MapImp?}); and as a
tool to estimate the sampling completeness of networks (Souza \emph{et
al.} 2021). It has, similarly, received a number of extensions,
including the ability to account for interaction strength (Magrach
\emph{et al.} 2017), the ability to handle probabilistic ecological
networks (Poisot \emph{et al.} 2016), and the integration into the Local
Contribution to Beta Diversity (Legendre \& De Cáceres 2013) approach to
understand how environment changes drive network dissimilarity (Poisot
\emph{et al.} 2017).

@@

In the following sections, I present a series of calculations aimed at
expressing the values of \(\beta_{os}\), \(\beta_{wn}\), and therefore
\(\beta_{st}\) as a function of species sharing probability (as a proxy
for mechanisms generating turnover), and link rewiring probability (as a
proxy for mechanisms generating differences in interactions among shared
species). These calculations are done using \texttt{Symbolics.jl}
(\textbf{Gowda2021HigSym?}), and subsequently transformed in executable
code for \emph{Julia} (\textbf{Bezanson2017JulFre?}), used to produce
the figures.

@@

@@

\leavevmode\hypertarget{ref-Koleff2003MeaBet}{}%
Koleff, P., Gaston, K.J. \& Lennon, J.J. (2003). Measuring beta
diversity for presence--absence data. \emph{Journal of Animal Ecology},
72, 367--382.

@@

>>>>

This approach has been widely adopted since its publication, with recent
examples using it to understand the effect of fire on pollination
systems (Baronio \emph{et al.} 2021); the impact of rewiring on
spatio-temporal network dynamics (Campos-Moreno \emph{et al.} 2021); the
effects of farming on rural and urban landscapes on species interactions
(Olsson \emph{et al.} 2021); the impact of environment gradients on
multi-trophic metacommunities (Ohlmann \emph{et al.} 2018); and as a
tool to estimate the sampling completeness of networks (Souza \emph{et
al.} 2021). It has, similarly, received a number of extensions,
including the ability to account for interaction strength (Magrach
\emph{et al.} 2017), the ability to handle probabilistic ecological
networks (Poisot \emph{et al.} 2016), and the integration into the Local
Contribution to Beta Diversity (Legendre \& De Cáceres 2013) approach to
understand how environment changes drive network dissimilarity (Poisot
\emph{et al.} 2017).

@@

In the following sections, I present a series of calculations aimed at
expressing the values of \(\beta_{os}\), \(\beta_{wn}\), and therefore
\(\beta_{st}\) as a function of species sharing probability (as a proxy
for mechanisms generating turnover), and link rewiring probability (as a
proxy for mechanisms generating differences in interactions among shared
species). These calculations are done using \texttt{Symbolics.jl} (Gowda
\emph{et al.} 2021), and subsequently transformed in executable code for
\emph{Julia} (\textbf{Bezanson2017JulFre?}), used to produce the
figures.

@@

\leavevmode\hypertarget{ref-Gowda2021HigSym}{}%
Gowda, S., Ma, Y., Cheli, A., Gwozdz, M., Shah, V.B., Edelman, A.,
\emph{et al.} (2021). High-performance symbolic-numerics via multiple
dispatch. \emph{arXiv:2105.03949 {[}cs{]}}.

@@

\leavevmode\hypertarget{ref-Koleff2003MeaBet}{}%
Koleff, P., Gaston, K.J. \& Lennon, J.J. (2003). Measuring beta
diversity for presenceabsence data. \emph{Journal of Animal Ecology},
72, 367--382.

@@

\leavevmode\hypertarget{ref-Ohlmann2018MapImp}{}%
Ohlmann, M., Mazel, F., Chalmandrier, L., Bec, S., Coissac, E., Gielly,
L., \emph{et al.} (2018). Mapping the imprint of biotic interactions on
\textbackslash beta-diversity. \emph{Ecology Letters}, 21, 1660--1669.
